Epilepsy GLMM example

### 2023-02-15 src/epil/epil.Rmd
Attempts to debug Laplace

```{r}
aghq_lognormconst <- fit11$normalized_posterior$lognormconst

lognormconsts <- purrr::map(laplace_x, function(x) x$quad$normalized_posterior$lognormconst)

@@

>>>>

```{r}
aghq_lognormconst <- fit11$normalized_posterior$lognormconst
lognormconsts <- purrr::map(laplace_x, function(x) x$quad$normalized_posterior$lognormconst)

@@

```{r}
#' Compute Laplace marginals with new method
```
